Response to reviewers

### 2025-01-21 Analysis/01_Simulating_spaces_and_stressors.Rmd
updated figure plots

## We can then visualise the simulated data (just two show the process)
par(mfrow = c(2, 1))
plot(simulated_data, main = "The simulated BM through time")
plot(simulated_data, main = "The 2D BM", trait = c(1,2))

@@

## First line
plot.text.box("A) Tree and trait\nsimulation:", cex = 2)
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (1D)", col = c(tips = "blue", "nodes" = "lightgrey"), ylab = "Trait 1")
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (2D)", col = c("lightgrey", "blue"), trait = c(1,2), xlab = "Trait 1", ylab = "Trait 2")

>>>>

## We can then visualise the simulated data (just two show the process)
par(mfrow = c(2, 1))
plot(simulated_data, main = "The simulated BM through time")
plot(simulated_data, main = "The 2D BM", trait = c(1,2), col = c("nodes" = "grey", "tips" = "blue"))

@@

## First line
plot.text.box("A) Tree and trait\nsimulation:", cex = 2)
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (1D)", col = c("tips" = "blue", "nodes" = "lightgrey"), ylab = "Trait 1")
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (2D)", col = c("tips" = "blue", "nodes" = "lightgrey"), trait = c(1,2), xlab = "Trait 1", ylab = "Trait 2")

### 2025-01-21 Manuscript/ecography_reponse_letter_2.tex
updated figure plots

% TODO: add colour legend to the plot
% TODO: distinguish between the two scalings in the figure
% TODO: expand scaling explanation in the caption

>>>>

We've now added the colour legend to the plot figure and removed the mention to the scaled metrics in the legend.
As requested by this reviewer, we now only display the raw metrics scored (in the supplementaries) and the scaled and null centered metrics scores (in the manuscript and in the supplementaries).
